---
title: '"apply" in R'
author: "Yan Zhizhi"
date: "Thursday, January 01, 2015"
output: html_document
---

source: https://nsaunders.wordpress.com/2010/08/20/a-brief-introduction-to-apply-in-r/

Content:
1.apply
2.

#1. apply
apply 将函数应用于array或matrix的边际   
返回vector或array或list
```{r}
# create a matrix of 10 rows x 2 columns
m <- matrix(c(1:10, 11:20), nrow = 10, ncol = 2)
# mean of the rows
apply(m, 1, mean)
# mean of the columns
apply(m, 2, mean)
# divide all values by 2
apply(m, 1:2, function(x) x/2)
```

#2. by
by类似于tapply，可以对数据做分组处理 
它是对tapply的封装   
作用于数据框
```{r}
attach(iris)
head(iris)
# get the mean of the first 4 variables, by species
by(iris[, 1:4], Species, colMeans)
```

#3. eapply
该函数作用于一个环境的所有变量，以list的方式返回结果   
```{r}
# a new environment
e <- new.env()
# two environment variables, a and b
e$a <- 1:10
e$b <- 11:20
# mean of the variables
eapply(e, mean)
```

#4.lapply
该函数返回与输入的元素X相同长度的list，list里的元素是将函数作用于X中对应的每个元素得到的结果   
```{r}
# create a list with 2 elements
l <- list(a = 1:10, b = 11:20)
# the mean of the values in each element
lapply(l, mean)
# the sum of the values in each element
lapply(l, sum)
```

##4.1 sapply
sapply视情况返回向量或者矩阵   
That simply means that if lapply would have returned a list with elements $a and $b, sapply will return either a vector, with elements [[‘a’]] and [[‘b’]], or a matrix with column names “a” and “b”.
```{r}
# create a list with 2 elements
l <- list(a = 1:10, b = 11:20)
# mean of values using sapply
l.mean <- sapply(l, mean)
# what type of object was returned?
class(l.mean)
l.mean
```

##4.2 vapply
返回的是数组，数组的列名是原列表的元素名
```{r}
l <- list(a = 1:10, b = 11:20)
# fivenum of values using vapply
l.fivenum <- vapply(l, fivenum, c(Min.=0, "1st Qu."=0, Median=0, "3rd Qu."=0, Max.=0))
class(l.fivenum)
l.fivenum
```

##4.3 replicate 
usually involve random number generation    
2个强制参数：the number of replications and the function to replicate
1个可选参数：simplify = T, tries to simplify the result to a vector or matrix
```{r}
m1 <- replicate(5, rnorm(5)); m1
m2 <- replicate(5, rnorm(5), simplify = F);m2
class(m1); class(m2)
```

#5. mapply
不太好描述。。我的理解是这个函数可以把多个列的对应位置的元素作为某个函数的参数来进行操作   
```{r}
l1 <- list(a = c(1:10), b = c(11:20))
l2 <- list(c = c(21:30), d = c(31:40))
l1; l2
# sum the corresponding elements of l1 and l2
mapply(sum, l1$a, l1$b, l2$c, l2$d)
```

#6. rapply
该函数是lapply的一个循环版本。。。其实是用不同的方式将函数应用于list上
```{r}
# let's start with our usual simple list example
l <- list(a = 1:10, b = 11:20); l
# log2 of each value in the list
rapply(l, log2)
# log2 of each value in each list
rapply(l, log2, how = "list")
# what if the function is the mean?
rapply(l, mean)
rapply(l, mean, how = "list")
```

#7. tapply
这个函数也可以用来对数据进行分组处理，与by有些类似   
```{r}
attach(iris)
# mean petal length by species
tapply(iris$Petal.Length, Species, mean)
#回顾一下by
by(iris$Petal.Length, Species, mean)
```