---
title: "John Hopkins_Regression Models_20141207"
author: "Yan Zhizhi"
date: "Sunday, December 07, 2014"
output: html_document
---
vedio 01-02 some basic definition -- notation - 9min  
关于SSE, MSE, RMSE等
vedio 01-03 General least squares for linear equations - 22min
讲了最小二乘法，一元线性回归的斜率和截距的计算方法
vedio 01-04 Historical side note, Regression to Mediocrity - 15min
讲了一个简单的回归案例，画了个图
vedio 01-05 Statistical Regression Linear Models - 18min

vedio 01-06 Residuals and residual variation -23min

###check our calculations on Intercept and Slope
```{r, message=FALSE}
library(UsingR);data(galton)
x <- galton$child
y <- galton$parent
beta1 <- cor(y,x) * sd(y)/sd(x)
beta0 <- mean(y) - beta1 * mean(x)
rbind(c(beta0, beta1), coef(lm(y ~ x)))
```
###标准化后的父亲与儿子的身高，看相关关系
```{r}
data(father.son)
#normalize the data
y <- (father.son$sheight - mean(father.son$sheight)) / sd(father.son$sheight)
x <- (father.son$fheight - mean(father.son$fheight)) / sd(father.son$fheight)
rho <- cor(x,y)
myPlot <- function(x,y){
  plot(x,y, xlab = "Father's height, normalized",
       ylab = "Son's height, normalized",
       xlim = c(-3,3), ylim = c(-3, 3),
       bg = "lightblue", col = "black", cex = 1.1, pch = 21,
       frame = FALSE)
}
myPlot(x,y)
abline(0,1) #if there were perfect correlation
abline(0, rho, lwd = 2, col = "red") #father predicts son
abline(0, 1/rho, lwd = 2, col = "green") #son predicts father, son on vertical axis
abline(h = 0); abline(v = 0) #reference lines for no relationship

#用ggplot2画图 
library(ggplot2)
g = ggplot(data.frame(x, y), aes(x = x, y = y))
g = g + geom_point(size = 5, alpha = .2, colour = "black")
g = g + geom_point(size = 4, alpha = .2, colour = "red")
g = g + geom_vline(xintercept = 0)
g = g + geom_hline(yintercept = 0)
g = g + geom_abline(position = "identity")
g = g + geom_abline(intercept = 0, slope = rho, size = 2)
g = g + geom_abline(intercept = 0, slope = 1 / rho, size = 2)
g = g + xlab("Father's height, normalized")
g = g + ylab("Son's height, normalized")
g
```

###01-05 statistical linear regression model

#### Plot of the data
```{r, message = FALSE, fig.height=5,fig.width=5}
library(UsingR)
data(diamond)
library(ggplot2)
g = ggplot(diamond, aes(x = carat, y = price))
g = g + xlab("Mass (carats)")
g = g + ylab("Price (SIN $)")
g = g + geom_point(size = 7, colour = "black", alpha=0.5)
g = g + geom_point(size = 5, colour = "blue", alpha=0.2)
g = g + geom_smooth(method = "lm", colour = "black")
g
```

#### Fitting the linear regression model
```{r}
fit <- lm(price ~ carat, data = diamond)
coef(fit)
```

#### Getting a more interpretable intercept
```{r, echo = TRUE}
fit2 <- lm(price ~ I(carat - mean(carat)), data = diamond)
coef(fit2)
```

#### Changing scale
```{r, echo = TRUE}
fit3 <- lm(price ~ I(carat * 10), data = diamond)
coef(fit3)
```

###01-06 Residuals and residual variation

```{r}
library(UsingR)
data(diamond)
y <- diamond$price; x <- diamond$carat; n <- length(y)
fit <- lm(y ~ x)
e <- resid(fit)
yhat <- predict(fit)

#观察残差随X的变化   Residuals versus X
#似乎plot(fit)这个指令画出的四幅图里的第一幅应该是这个吧。。。
plot(x, e,  
     xlab = "Mass (carats)", 
     ylab = "Residuals (SIN $)", 
     bg = "lightblue", 
     col = "black", cex = 2, pch = 21,frame = FALSE)
abline(h = 0, lwd = 2)
for (i in 1 : n) 
  lines(c(x[i], x[i]), c(e[i], 0), col = "red" , lwd = 2)
```

####关于回归结果相同，但实际分布天差地别的一个案例
```{r}
data(anscombe)
example(anscombe)
```